% Tim Dennis' Resume
% Created: 14 Jan 2012
% Last Modified: 14 Jul 2012

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{plain} %was empty
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Tim Dennis}
\newcommand{\addr}{468 41St Street, Apt. B, Oakland, CA  94609}
\newcommand{\phone}{(510)842-7061}
\newcommand{\email}{dennis.tim@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}

\thispagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

  \resbigitem{UC Berkeley School of Information}{Berkeley, CA (May, 2006)}{M.S. of Information Management and Systems}

  \resbigitem{Millsaps College}{Jackson, MS (June, 1990)}{B.A. in Sociology}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

	\begin{ressubsec}{Library Data Lab}{Berkeley, CA}{Research Technology and Services Specialist (August, 2006--present)}
		\ressubitem{Build numerous Library websites in Drupal implementing diverse domain requirements including re-purposing \&  presenting  bibliographic data, campus authentication, and supporting library workflows.}
		\ressubitem{Consult with multiple internal Library units providing best-practice advice on Drupal site building, module selection \& configuration, server setup \& configuration, and theme development.}
		\ressubitem{Coordinate the Library Technology Training Program for over 400 staff members.}
		\ressubitem{Provide numeric data/statistical information consultation to students and faculty.}
		\ressubitem{Write Python scripts for data acquisition, manipulation and cleaning.}
		\ressubitem{Offer training courses to library staff on various technologies including Drupal.}
	\end{ressubsec}

	\begin{ressubsec}{UC Berkeley Library}{Berkeley, CA}{Web, Electronic, and Government/Numeric Data Specialist (May, 2002 - August, 2006)}
		\ressubitem{Selected, installed, maintained, \& customized web collaboration applications including wikis, blogs, \& messaging.}
		\ressubitem{Administered library development server including creating and managing accounts, monitoring logs, updating applications, and monitoring usage and security logs.}
		\ressubitem{Managed multiple cross-functional teams in developing and implementing new library web based services.}
		\ressubitem{Trained users and created instruction materials on adoption of new collaboration tools.}
		\ressubitem{Provided numeric data/government information reference to students and faculty via IM, email \& face-to-face.}		
	\end{ressubsec}
	
	\begin{ressubsec}{Infromation \& Service Design (formerly Center for Document Engineering)}{Berkeley, CA}{Usability Specialist/Researcher (September, 2005 - May, 2006)}
	  \ressubitem{Completed needs assessment for academic web pattern library application.}
	  \ressubitem{Developed a pattern library using participatory design techniques, personas, scenarios, lo-fi and hi-fi prototyping.}
	  \ressubitem{Conducted usability analysis and user testing on patterns and library interfaces.}
	  \ressubitem{Developed the front-end for web pattern application using parallel development environments in JSP, XSL, XML, \& BerkeleyDB XML and PHP, CSS, XHTML, MYSQL, \& JavaScript.}
	\end{ressubsec}
\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

	\begin{reslist}{Drupal (id: jt14den):}

		\ressubitem{Intermediate site building knowledge: CCK, Views, Panels, User management }

    \ressubitem{Intermediate use of Features to maintain DB configuration}

		\ressubitem{Novice themer: Use base theme/sub-theme \& modify/extend templates \& CSS}

    \ressubitem{Intermediate development skills: Drush tools for installing, configuring, \& managing sites, Drush+git for features}
    
	\end{reslist}

	\begin{reslist}{Programming/Web Development:}

		\ressubitem{Intermediate scripting skills: Python, PHP}

		\ressubitem{Intermediate HTML \& CSS}
		
		\ressubitem{Intermediate SQL}
		
		\ressubitem{Databases: MySQL, SQLite}
		
		\ressubitem{Basic version control skills: SVN, Git (github id: jt14den)}

	\end{reslist}
	
	\begin{reslist}{Sys Admin}
	
	  \ressubitem{Intermediate unix/linux systems \& tools}
	  
    \ressubitem{Intermediate understand Linux package managers}
    
    \ressubitem{Intermediate experience with LAMP configuration \& server setup}
	
	\end{reslist}
	
	\begin{reslist}{Statistical Software}
	
	  \ressubitem{Novice STATA \& R user}
	  
	\end{reslist}
	
  \begin{reslist}{UX}
	
	  \ressubitem{Information Architecture: Taxonomy development, card-sort}
  
	  \ressubitem{User Research: User interviewing, task analysis, persona \& scenario development}
	  
	  \ressubitem{Design: Paper prototyping, wire-frames}

    \ressubitem{Keep up-to-date by attending various UIE webinars}
    
	\end{reslist}
	
	\begin{reslist}{Communication}

    \ressubitem{Offered over 15 workshops on technical topics for the library staff training program}

    \ressubitem{Demonstrated ability translate user needs to programmers and likewise, to translate technical topics to novice users}

    \ressubitem{Highly effective in cross-functional team settings}

  \end{reslist}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Selected Instruction}

	\resitem{\textit{Getting started in Drupal}. UC Berkeley LibTech. 2010.}

	\resitem{\textit{Using the Content Construction Kit (CCK) in Drupal}. UC Berkeley LibTech. 2010.}

	\resitem{\textit{Drupal Study Group}. UC Berkeley LibTech. 2009.}

	\resitem{\textit{Intro to Google Analytics}. UC Berkeley LibTech. 2009.}

	\resitem{\textit{Google Data API}. IASSIST 2008. May 27, 2008.}

\end{ressection}


\end{document}
